\input{article preambles}

\setcounter{section}{-1}

\input{commands}

\begin{document}

    \title{Quiver varieties}
    
    \author{Dat Minh Ha}
    \maketitle
    
    \begin{abstract}
    
    \end{abstract}
    
    {
    \hypersetup{} 
    %\dominitoc
    \tableofcontents %sort sections alphabetically
    }

    \section{Introduction}
        Nakajima's quiver varieties are certain smooth (not necessarily affine) complex algebraic varieties associated with quivers. These varieties have been used by Nakajima to give a geometric construction of universal enveloping algebras of Kac-Moody Lie algebras (as well as a construction of quantized enveloping algebras for affine Lie algebras) and of all irreducible integrable (e.g., finite dimensional) representations of those algebras.

        A connection between quiver representations and Kac-Moody Lie algebras was first discovered by Ringel around 1990. Ringel produced a construction of $\rmU_q(\n^+)$, the positive part of the quantized enveloping algebra $\rmU_q(\g)$ of a Kac-Moody Lie algebra $\g$, in terms of a Hall algebra associated with an appropriate quiver. Shortly afterwards, Lusztig combined Ringel's ideas with the powerful technique of perverse sheaves to construct a canonical basis of $\rmU_q(\n^+)$.
        
        The main advantage of Nakajima's approach (as opposed to the earlier one by Ringel and Lusztig) is that it yields a geometric construction of the whole algebra $\rmU(\g)$ rather than its positive part. At the same time, it also provides a geometric construction of simple integrable $\rmU(g)$-modules. Nakajima's approach also yields a similar construction of the algebra $\rmU_q(\g[v^{\pm 1}])$ and its simple integrable representations.

    \section{Nakajima's quiver varieties}
        \begin{convention}
            We work over $\bbC$, though this may be replaced by any algebraically closed field of characteristic $0$.
        \end{convention}
        \begin{convention}[Quivers]
            When referring to \textbf{quivers}, often denoted by $Q := (I, E)$, we shall always mean a diagram of the form:
                $$
                    \begin{tikzcd}
                	{E} & {I}
                	\arrow["t"', shift right=2, from=1-1, to=1-2]
                	\arrow["s", shift left=2, from=1-1, to=1-2]
                    \end{tikzcd}
                $$
            in the category of sets. The functions $s, t: E \toto I$ are usually called the \textbf{source} and \textbf{target} maps respectively, while the sets $E, I$ are usually referred to as the sets of \textbf{directed edges} and of \textbf{vertices}; note also that unlike a (small) category, a quiver lacks a composition rule for its \say{morphisms}.

            Now, to any quiver $Q := (I, E)$, one can associate a free category $\<Q\>$ by freely adjoining all compositions of elements of $E$. The \textbf{path algebra} $\bbC Q$ of a quiver $Q$ is then algebra whose underlying vector space has $E$ as a basis, and whose multiplication is given by composition of arrows in $\<Q\>$. We caution the reader that while $\bbC Q$ is always an associative algebra\footnote{... as compositions of arrows in a category is associative by definition.}, it is unital if and only if $I$ is a finite set\footnote{Though $E$ may still be infinite, i.e. $\bbC Q$ can be infinite-dimensional}; namely, when $I$ is finite, the multiplicative identity of $\bbC Q$ will be $1_Q := \sum_{i \in Q_0} 1_i$, with $1_i$ denoting the identity arrows at the vertices $i \in I$.

            A \textbf{representation} of a quiver is nothing but a module over its path algebra. 

            Also, much like categories, quivers have \textbf{opposites}. Namely, if $Q := (I, E)$ is a quiver then $Q^{\op} := (I^{\op}, E^{\op})$ shall be determined by:
                $$\<Q^{\op}\> = \<Q\>^{\op}$$
        \end{convention}
        \begin{proposition}[Universal property of path algebras of finite quivers] \label{prop: universal_property_of_path_algebras_of_finite_quivers}
            Let $Q := (I, E)$ be a finite quiver.
            
            Firstly, let $\bbC I := \Maps(I, K)$ for the commutative $\bbC$-algebra of $\bbC$-valued functions on $I$, equipped with pointwise multiplication; note that this is a finite-dimensional and semi-simple $\bbC$-algebra that is isomorphic to $\bigoplus_{i \in I} \bbC$ with entry-wise multiplication and as such, let us write $1_i$ for the characteristic function supported on $\{i\} \subseteq I$.

            Secondly, write $\bbC E$ for the $\bbC I$-bimodule with underlying $\bbC$-vector space $\bbC^E$ and $\bbC I$-action given by:
                $$1_i \cdot e \cdot 1_j = \delta_{i, s(e)} \delta_{j, t(e)} e$$
            for all $e \in E$ and all $i, j \in I$. 

            Then, there shall exist an isomorphism of associative and unital $\bbC$-algebras:
                $$\bbC Q \cong \rmT_{\bbC I}( \bbC E )$$
            betweent the path algebra of $Q$ and the tensor algebra of the $\bbC I$-bimodule $\bbC E$ regarded as a $\bbC$-algebra. 
        \end{proposition}
            \begin{proof}
                
            \end{proof}

        \begin{convention}
            Symplectic geometry will be a prominent tool in the analysis of quiver varieties. The word \say{symplectic} ought to always be understood in the algebraic sense. 
        \end{convention}
    
        \subsection{Moduli spaces of quiver representations}
            
    
    \addcontentsline{toc}{section}{References}
    \printbibliography

\end{document}